Interval-Valued Quantum Probabilities: Contextuality and the Born Rule

### 2017-05-13 prop_letter.tex
prop_letter.tex \section{Fuzzy Measurements} Fix corresponding states...

As an example, consider a three-dimensional Hilbert space with
orthonormal basis $\{\ket{0},\ket{1},\ket{2}\}$ and an observable $Q$
with spectral decomposition $\proj{0} + 2\,\proj{1} +
3\,\proj{2}$. Here are two fragments of valid probability measures
$\mu_1$ and $\mu_2$ that can associated with this space:
$\mu_1(\proj{0}) = 0.5$, $\mu_1(\proj{1}) = 0.5$,
$\mu_1(\proj{2}) = 0$, and $\mu_2(\proj{0}) = 0.5$,
$\mu_2(\proj{1}) = 0$, $\mu_2(\proj{2}) = 0.5$. By the Born rule,
the first probability measure corresponds to the quantum system being
in the state $(\ket{0}\pm\ket{1})/\sqrt{2}$ and the second corresponds
to the quantum system being in the state
$(\ket{0}\pm\ket{2})/\sqrt{2}$. The expectation value of the observable
in the first case is 1.5 and in the second it is 2.

@@

>>>>

As an example, consider a three-dimensional Hilbert space with
orthonormal basis $\{\ket{0},\ket{1},\ket{2}\}$ and an observable $Q$
with spectral decomposition $\proj{0} + 2\,\proj{1} +
3\,\proj{2}$. Here are two fragments of valid probability measures
$\mu_1$ and $\mu_2$ that can associated with this space:
$\mu_1(\proj{0}) = 0.5$, $\mu_1(\proj{1}) = 0.5$,
$\mu_1(\proj{2}) = 0$, and $\mu_2(\proj{0}) = 0.5$,
$\mu_2(\proj{1}) = 0$, $\mu_2(\proj{2}) = 0.5$. By the Born rule,
the first probability measure corresponds to the quantum system being
in the state $(\ket{0}+\alpha\ket{1})/\sqrt{2}$ and the second corresponds
to the quantum system being in the state
$(\ket{0}+\alpha\ket{2})/\sqrt{2}$, where $|\alpha|=1$. The expectation value
of the observable in the first case is 1.5 and in the second it is 2.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Classical IVPMs}
